---
title: "Immunephenotypes of SARS-CoV-2-specific T cells"
author: "Group 4 - Marcus Göransson, Marie Christine Viuff, Signe Koggersbøl Skadsborg, Susana Patricia Hernandez, Yogesh Basavaraju"
date: "11 May 2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Materials and methods

- Bullet 1
- Bullet 2
- Bullet 3

## COVID-19 dataset

```{r cars, echo = TRUE}
summary(cars)
```

## Data wrangling

```{r, code=xfun::read_utf8('R/03_augment.R')}

```


## Results

```{r, code=xfun::read_utf8('04_analysis_i.R')}

```

## Results 2
```{r pressure}
plot(pressure)
```

## Conclusion
